---
title: "Human Freedom Index"
author: "Arpi Beshlikyan & Jazmine Toledo"
date: "July 11, 2019"
output: 
  powerpoint_presentation:
    reference_doc: ppt_template.pptx
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
load(file="hfi_cc_2018.RData")
```

## The Human Freedom Index 
"The Human Freedom Index presents the state of human freedom in the world based on a broad measure that encompasses personal, civil, and economic freedom."

The report is co-published by the Cato Institute, the Fraser Institute, and the Liberales Institut at the Friedrich Naumann Foundation for Freedom.
For more details on the Human Freedom Index Project, see <https://www.cato.org/human-freedom-index-new>.

## Project Topic
We will investigate the correlations between variables taken from the Human Freedom Index. In particular, we want to look at the following:

- Religious Freedom
- Violent conflicts
- Security and safety
- Press jailed
- Same-sex relationships

## Univariate summary of Independent Variable
- Religious Freedom:
```{r echo=FALSE}
data<-hfi_cc_2018
summary(data$pf_religion)
```

## Univariate Summaries of Dependent Variables
- Violent conflicts:
```{r echo=FALSE}
summary(data$pf_ss_disappearances_violent)
```

- Security and safety:
```{r echo=FALSE}
summary(data$pf_ss)
```

## Univariate Summaries of Dependent Variables (cont.)
- Press jailed:
```{r echo=FALSE}
summary(data$pf_expression_jailed)
```
- Same-sex relationships:
```{r echo=FALSE}
summary(data$pf_identity_sex)
```

## Conclusion

In conclusion, with the given data we will explore the definition of freedom and on a larger scale attempt to gain a better understanding of its relationship to other social and economic phenomena. 


