---
title: "Human Freedom Index"
author: "Arpi Beshlikyan & Jazmine Toledo"
date: "July 11, 2019"
output: powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown
```{r}
data<-hfi_cc_2018
names(data)
summary(data$pf_ss_disappearances_violent)
summary(data$pf_ss_disappearances_organized)
summary(data$pf_ss_women_fgm)
summary(data$pf_ss_women)
summary(data$pf_ss)
summary(data$pf_expression_killed)
summary(data$pf_expresion_jailed)
summary(data$pf_identity_sex)
```

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

